A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
a bit more CM

In this section we briefly summarize balance equations of fine-strain hyperelastic continuum.

@@

Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$
is defined via the mapping $\gz x = \gz \varphi (\gz X,t)$.
The displacement field reads $\gz u = \gz x - \gz X$.
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \Grad \, \gz \varphi \equiv \gz I + \Grad \, \gz u$ is the deformation gradient.
For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz F; \gz X) \d V \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, $\mcl \psi$ denotes the strain-energy per unit reference volume and $\gz u$ should satisfy the prescribed Dirichlet boundary conditions $\gz u = \gz u^D$ on $\partial \mcl B_0^D := \partial \mcl B_0 \setminus \partial \mcl B_0^N \neq \emptyset $.

The principal of stationary potential energy requires that at the equilibriums the directional derivative with respect to the displacement $\gz u$
\begin{align}
\delta \mcl E =
\frac{\d}{\d \epsilon} \mcl E (\gz u + \epsilon \delta \gz u) \Bigr\rvert_{\epsilon=0}  = 0 \, .
\label{eq:stationary}
\end{align}
vanishes for all directions $\delta \gz u$ which satisfy homogeneous Dirichlet boundary conditions.
%
This leads to the following non-linear equation
\begin{align}
F(\gz u, \delta \gz u) =
\int_{\mcl B_0} \gz P : \Grad \, \delta \gz u \d V \,
-
\int_{\partial \mcl B_0^N} \gz T \cdot \delta \gz u \d S
= 0 \, ,
\end{align}
where $\gz P := \partial \mcl \psi / \partial \gz F$ is the Piola stress.

>>>>

In this section we briefly summarize balance equations of fine-strain hyperelastic continuum in Lagrangian (also known as referential) description.

@@

%
% Kinematics
%
Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$ at time $t$
is defined via the mapping $\gz \varphi_t: \mcl B \rightarrow \mathbb E^3$, which places material points of $\mcl B$ in Euclidean space $\mathbb E^3$.
The location of a material particle $\gz X$ is given by $\gz x = \gz \varphi_t (\gz X)$.
The displacement field reads $\gz u = \gz x - \gz X$.

%
% Deformation gradient
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \Grad \, \gz \varphi \equiv \gz I + \Grad \, \gz u$ is called deformation gradient.
The mapping has to be one-to-one and exclude a self penetration, consequently the Jacobian has to be positive $J = \det \gz F > 0$.
Deformation gradient can be split in the proper orthogonal rotation tensor $\gz R$ and the symmetric right $\gz U$ and left $\gz V$ stretch tensors as $\gz F = \gz R \gz U = \gz V \gz R$.
%
% strain measures
%
In what follows we characterize the material behavior using the Green-Lagrange strain tensor $\gz E:=\frac{1}{2}\left[\gz C - \gz I\right]$, where $\gz C$ is right Cauchy-Green tensor $\gz C := \gz F^T \cdot \gz F = \gz U^2$. Clearly $J = \sqrt{\det \gz C}$ and $\partial (\bullet)/\partial \gz E = 2\, \partial (\bullet)/\partial \gz C$.

For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz C) \d V \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, $\mcl \psi$ denotes the strain-energy per unit reference volume and $\gz u$ should satisfy the prescribed Dirichlet boundary conditions $\gz u = \gz u^D$ on $\partial \mcl B_0^D := \partial \mcl B_0 \setminus \partial \mcl B_0^N \neq \emptyset $.

The principal of stationary potential energy requires that at the equilibriums the directional derivative with respect to the displacement $\gz u$
\begin{align}
\delta \mcl E =
\frac{\d}{\d \epsilon} \mcl E (\gz u + \epsilon \delta \gz u) \Bigr\rvert_{\epsilon=0}  = 0 \, .
\label{eq:stationary}
\end{align}
vanishes for all directions $\delta \gz u$ which satisfy homogeneous Dirichlet boundary conditions.
%
This leads to the following non-linear equation
\begin{align}
F(\gz u, \delta \gz u) =
\int_{\mcl B_0} \gz S : \delta \gz E \d V \,
-
\int_{\partial \mcl B_0^N} \gz T \cdot \delta \gz u \d S
= 0 \, ,
\end{align}
where $\gz S := 2\, \partial \mcl \psi / \partial \gz C$ is the second Piola-Kirchhoff stress tensor.
